\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2016-02-15 doc/USER_MANUAL/04_creating_databases.tex
added notes about attenuation
larger figure in the manual (for an important one)

\item [{\texttt{gll}}] For a user-specified isotropic model which uses
external binary files for $v_{p}$, $v_{s}$ and $\rho$. Binary files
are given in the same format as when outputted by the \texttt{xgenerate\_databases}
executable when using option \texttt{SAVE\_MESH\_FILES}. These binary
files define the model parameters on all GLL points which can be used
for iterative inversion procedures. Note that for simulation setups with attenuation, 
it will also read in the external binary mesh files for $Q_{\kappa}$ and $Q_{\mu}$.

@@

@@

%%
\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[width=3in]{figures/how_to_use_PML_when_a_tomographic_velocity_model_is_used.png}
\par\end{centering}

>>>>

\item [{\texttt{gll}}] For a user-specified isotropic model which uses
external binary files for $v_{p}$, $v_{s}$ and $\rho$. Binary files
are given in the same format as when outputted by the \texttt{xgenerate\_databases}
executable when using option \texttt{SAVE\_MESH\_FILES}. These binary
files define the model parameters on all GLL points which can be used
for iterative inversion procedures. Note that for simulation setups with attenuation,
it will also read in the external binary mesh files for $Q_{\kappa}$ and $Q_{\mu}$.
Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp. To convert one to the other see doc/note\_on\_Qkappa\_versus\_Qp.pdf and utils/attenuation/conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90.

@@

Note that Qmu is always equal to Qs, but Qkappa is in general not equal to Qp. To convert one to the other see doc/note\_on\_Qkappa\_versus\_Qp.pdf and utils/attenuation/conversion\_from\_Qkappa\_Qmu\_to\_Qp\_Qs\_from\_Dahlen\_Tromp\_959\_960.f90.

@@

%%
\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[width=6in]{figures/how_to_use_PML_when_a_tomographic_velocity_model_is_used.png}
\par\end{centering}
